---
title: "p8105_hw1_fs2968"
output: github_document
---

```{r echo=FALSE, message = FALSE}
#Loading necessary library and database
library(tidyverse) 
data("penguins", package = "palmerpenguins")

```

# Problem 1, Penguin Dataset Summary
The penguin dataset avaialble with the palmerpenguins package describes `r ncol(penguins)` different characteristics of penguins for a total of `r nrow(penguins)` penguins. These characteristics are measured in different ways as well. The species of penguin, the island of origin, and sex are categorical variables with values like Adelie, Torgersen, and female respectively. The bill length and depth are measured as doubles to the first decimal place. Lastly, flipper length, body mass index, and year are measured as integers. We can do some simple statistics with this data set to gain insight, like calculating the mean of the penguins flipper length after removing NA values: `r mean((pull(penguins, flipper_length_mm)), na.rm=TRUE)`. 


# Plotting Data
Here, we can plot some of our data to help visualize it. For example, below we plot bill length vs flipper length:

```{r echo=FALSE, message=FALSE} 
#Creating a seperate database with removed na values
penguins_plot <- penguins %>% drop_na(bill_length_mm, flipper_length_mm)
#Plotting 2 columns of data in a scattor plot, colored by species
ggplot(penguins_plot, aes(x = bill_length_mm, y = flipper_length_mm, color=species)) + geom_point()
ggsave("scatterplot.pdf")
```

In the graph above, we have bill length on the x-axis and flipper length on the y-axis, showing the relation of these two characteristics color-differentiated by species. We can observe that the Adelie Penguins on average have the small flipper length and small bill length, the Chinstrap penguins have small flipper length but much larger bill length, and Gentoo penguins have large flipper length and large bill length. 

# Problem 2, Building dataframe

```{r}

df = tibble(
  rand_sample = rnorm(10),
  log_vec = rand_sample > 0,
  char_vec = c("a","b","c","d","e","f","g","h","i","k"),
  factor_vec = factor(rep(c("low", "medium", "high"), length.out= 10))
)

mean_out <- c(mean(pull(df, rand_sample)), mean(pull(df, log_vec)), mean(pull(df, char_vec)), mean(pull(df, factor_vec)))

mean_out 

as.numeric(pull(df, log_vec))
as.numeric(pull(df, char_vec))
as.numeric(pull(df, factor_vec))

```









